Replication of Hills 2009

### 2018-07-26 Hills2009Replication.Rmd
Changed network generation method, breaking changes for Hills2009Replication.

# Networks

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(broom) # converts R function outputs to tidy data frames
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(kableExtra) # table formatting
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(tidygraph)
library(doParallel)
library(networkD3)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

# knit_print.data.frame <- lemon_print # use kable when displaying tibbles in knit
```

@@

Hills selected nouns from the Todler version of the MacArthur-Bates Communicative Developmental Inventory. This includes nouns which were aquired by 50% of children by 30 months.

*This needs to be fixed to match Hills exactly*.
```{r warning=FALSE}
# We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.

vocab <- make_vocab_dataframe(lang="English (American)",
                              lang_form = "WS",
                              lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition()

features <- load_features()

vocab <- vocab %>%
  filter(age <= 30) %>%
  filter(uni_lemma %in% features$uni_lemma)
```

@@

Next, we construct networks following the example of Hills. Using vocabulary obtained by 30 months and the same MacRae features as Hills, we construct networks from perceptual and conceptual features. We consider only words for which some feature data is available (though not necessarily perceptual or conceptual), and track the number of features that generate each edge.

@@

@@

Compared to Hills' 130 nouns that overlapped the MacRae data and vocabulary data, we have `r vcount(perceptual_network)` nouns.

*TODO extend*

@@

## Visualize Networks
```{r out.width = '100%'}
par(mfcol=c(3, 3), mar=c(0.5,0.5,0.5,0.5))
for (n in networks[c(TRUE, TRUE, TRUE, FALSE, # display networks for w=1,2,3
                     TRUE, TRUE, TRUE, FALSE,
                     TRUE, TRUE, TRUE, FALSE)]) {
  plot_network(n, remove_isolated = TRUE, frame=FALSE)
}
```

>>>>

# Methods

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(broom) # converts R function outputs to tidy data frames
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(kableExtra) # table formatting
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(tidygraph)
library(doParallel)
library(networkD3)
library(ForceAtlas2)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
```

@@

Hills selected nouns from the Todler version of the MacArthur-Bates Communicative Developmental Inventory. This includes nouns which were aquired by 50% of children by 30 months. *This needs to be fixed to match Hills exactly*.

```{r warning=FALSE}
# We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.

full_vocab <- make_vocab_dataframe(lang="English (American)",
                              lang_form = "WS",
                              lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition()
```

The initial vocabulary contains `r nrow(full_vocab)` (compared to Hills' 312).

## Features

Features taken from McRae et al. (2005), in which features were collected for 541 nouns from 725 adults, with 30 adults providing  14 features for each noun.

```{r warning=FALSE}
features <- load_features()

vocab <- full_vocab %>%
  filter(age <= 30) %>%
  filter(uni_lemma %in% features$uni_lemma) %>%
  distinct(uni_lemma, .keep_all = TRUE)
```

Only the words for which feature data are available are considered, an overlap of `r nrow(vocab)` in our data compared to Hills' 130.

@@

Using vocabulary obtained by 30 months and the same MacRae features as Hills, we construct networks from perceptual and conceptual features. We track the number of features that generate each edge.

@@

# Results

## The Full Network

### Network statistics and small-world analyses

```{r}
# testing dense layout
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

plot_network(full_network %E>% filter(shared >= 2), remove_isolated = TRUE, labels=TRUE, frame=TRUE)
```

The full network is shown in the following figure, for w = 1, 2, 3, and 4.

```{r out.width = '100%'}
full_networks = list()
for (w in 1:4) {
  full_networks[[w]] = full_network %E>%
    filter(shared >= w)
}

#par(mfcol=c(2, 2), mar=c(0.5,0.5,0.5,0.5))
for (network in full_networks) {
  plot_network(network, remove_isolated = FALSE, labels=TRUE, frame=TRUE)
}
```

@@

@@

### 2018-07-26 Main.Rmd
Changed network generation method, breaking changes for Hills2009Replication.

---
output:
  html_document: default
  pdf_document: default
---
# Basic Network Analysis of Wordbank Data

@@

List of libraries
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(boot) # functions for bootstrapping
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(directlabels) # direct labeling of data in plots
library(stringr) # common string operations
library(lmtest) #  diagnostic checking in linear regression models
library(rwebppl) # interface to probabilistic programming language WebPPL
library(jsonlite) # JSON parser
library(nlme) # gaussian linear and nonlinear mixed-effects models
library(feather) # read and write fast lightweight binary columnar data
library(broom) # converts R function outputs to tidy data frames
library(HDInterval) # calculate highest density intervals of objects w/ pdf
library(BBmisc) # misc helper functions
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(doParallel)
library(networkD3)
```

Import helper functions and configure RMarkdown
```{r echo=TRUE, warning=FALSE, message=FALSE}
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

knit_print.data.frame <- lemon_print # use kable when displaying tibbles in knit
```

Create vocab 
```{r echo=TRUE, warning=FALSE, message=FALSE}
# Import data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. The "defintion" is the word, the "unilemma"" is the translation in English.

# We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication

vocab <- make_vocab_dataframe(lang="English (American)",
                              lang_form = "WS",
                              lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition() # %>%
  # distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
```

Build networks
```{r}
assoc_network <- function(vocab, max_age) {
  vocab_up_to_age = filter(vocab, age <= max_age)
  assoc_links <- make_assoc_pairs(lemma_list = vocab_up_to_age) %>%
    filter(link==1) %>%
    select(item, pair, item.definition, pair.definition)
  graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=vocab_up_to_age) %>%
    simplify() %>%
    set.graph.attribute("name", "Assoc") %>%
    set.graph.attribute("age", max_age)
  return(graph)
}

feature_network <- function(vocab, max_age, shared_threshold) {
  vocab_up_to_age = filter(vocab, age <= max_age)
  feature_links <- make_feature_pairs(lemma_list = vocab_up_to_age) %>%
    filter(shared >= shared_threshold) %>%
    select(item, pair, item.definition, pair.definition)
  graph <- graph_from_data_frame(feature_links, directed=FALSE, vertices=vocab_up_to_age) %>%
    simplify() %>%
    set.graph.attribute("name", "Feature") %>%
    set.graph.attribute("age", max_age)
  return(graph)
}

ages <- vocab$age %>% unique() %>% sort()
assoc_networks <- list()
feature_networks <- list()
for (age in ages) {
  assoc_networks <- append(assoc_networks, list(assoc_network(vocab, age)))
  feature_networks <- append(feature_networks, list(feature_network(vocab, age, 1)))

}
```

## Network Analysis

### Large-Scale Structure of Networks

a la Steyvers 2005

```{r, results='asis'}
network_properties <- function(networks) {
  return( tibble(
  names = map_chr(networks, ~ .x$name),
  ages = map_dbl(networks, ~ .x$age) %>%
    as.integer(),
  vertices = map_int(networks, vcount),
  edges = map_dbl(networks, ecount) %>%
    as.integer(), # for some reason igraph ecount returns double
  avg_degree = map(networks, degree) %>%
    map_dbl(mean),
  avg_shortest_path = map_dbl(networks, mean_distance),
  diameter = map_dbl(networks, diameter) %>%
    as.integer(),
  clustering_coefficient = map_dbl(networks, transitivity),
  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
  diameter_random = 0,
  clustering_coefficient_random = 0) )
}

network_properties(assoc_networks) # improve formatting
network_properties(feature_networks)
```

Visualize Networks
```{r}
plot_network <- function(g, remove_isolated=FALSE) {
  if (remove_isolated) {
    g <- delete.vertices(g, degree(g)==0)
  }

  plot(g, vertex.label=V(g)$uni_lemma, vertex.shape="none")
}

g <- assoc_networks[[6]]
plot_network(g, remove_isolated = FALSE)

plot(g,vertex.size=.01,vertex.label.cex=.8,
     layout=layout.fruchterman.reingold(g, niter=10000, 
                                        area=40*vcount(g)^2),
     edge.width=E(g)$weight)
```

Test Clique Percolation
```{r}
### Register Parallelisation (used by clique.community.opt.par())
cl <- makeCluster(4)
registerDoParallel(cl)
getDoParWorkers()

### Loading Benchmarks
#1 
g <- graph(c(1,2,1,3,1,4,2,3,3,4,4,5,4,6,5,6,5,8,5,7,6,8,6,7,7,8,7,9), directed=F)
#2
g <- make_graph("Zachary") #the karate network

#Execution of the different implementation of the algorithm
ptm <- proc.time()
res1<-clique.community(g,3)
proc.time() - ptm
ptm <- proc.time()
res2<-clique.community.opt(g,3)
proc.time() - ptm
ptm <- proc.time()
res3<-clique.community.opt.par(g,3)
proc.time() - ptm

identical(res1,res2)
identical(res2,res3)

### PLOT

#which one? the outcome is always the same
res <- res3

## Paint them to different colors
colbar <- rainbow( length(res)+1 )
for (i in seq(along=res)) {
  V(g)[ res[[i]] ]$color <- colbar[i+1]
}

## Paint the vertices in multiple communities to red
V(g)[ unlist(res)[ duplicated(unlist(res)) ] ]$color <- "red"

## Plot with the new colors
plot(g, layout=layout_with_fr, vertex.label=V(g)$name)

#REAL PERFORMANCE TEST
require(microbenchmark)
b1<-microbenchmark(t1<-clique.community(g,3),times = 100,unit = 'ms')
b2<-microbenchmark(t2<-clique.community.opt(g,3),times = 100,unit = 'ms')
b3<-microbenchmark(t2<-clique.community.opt.par(g,3),times = 100,unit = 'ms')
rbind(b1,b2,b3)
mean(b1$time)/mean(b2$time)
mean(b2$time)/mean(b3$time)
mean(b1$time)/mean(b3$time)
```

Initial Clique Analysis
```{r}
age <- 20
g <- assoc_networks[[age - 15]]
g <- delete.vertices(g, degree(g)==0)
res <- clique.community.opt(g,3)

## Paint them to different colors
colbar <- rainbow( length(res)+1 )
for (i in seq(along=res)) {
  V(g)[ res[[i]] ]$color <- colbar[i+1]
}

## Paint the vertices in multiple communities to red
V(g)[ unlist(res)[ duplicated(unlist(res)) ] ]$color <- "red"

## Plot with the new colors
plot(g, layout=layout_with_fr, vertex.label=V(g)$uni_lemma)
```

Dynamic Visualization
```{r}
karate <- make_graph("Zachary")
wc <- cluster_walktrap(karate)
members <- membership(wc)

# Convert to object suitable for networkD3
karate_d3 <- igraph_to_networkD3(karate, group = members)

# Create force directed network plot
forceNetwork(Links = karate_d3$links, Nodes = karate_d3$nodes,
             Source = 'source', Target = 'target', NodeID = 'name',
             Group = 'group')
```

>>>>

---
title: "Replication of Hills 2009"
author: "Isaac Scheinfeld"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: default
---
# Background

...

# Networks

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(broom) # converts R function outputs to tidy data frames
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(kableExtra) # table formatting
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(tidygraph)
library(doParallel)
library(networkD3)
library(ForceAtlas2)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
```

## Nouns

We begin with roughly the same data used by Hills. *(TODO fix, get same data)*

```{r warning=FALSE}
# We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.

full_vocab <- make_vocab_dataframe(lang="English (American)",
                              lang_form = "WS",
                              lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition() %>%
  arrange(age) %>%            # keep first age for duplicates
  distinct(uni_lemma, .keep_all = TRUE) %>%
  select(uni_lemma, definition, age)
```

The initial vocabulary contains `r nrow(full_vocab)` (compared to Hills' 312).

## Perceptual & Conceptual Features

Features taken from McRae et al. (2005), in which features were collected for 541 nouns from 725 adults, with 30 adults providing  14 features for each noun.

```{r warning=FALSE}
features <- load_features()

hills_vocab <- full_vocab %>%
  filter(age <= 30) %>%
  filter(uni_lemma %in% features$Concept) # filter to words with features
```

To begin our analysis, we only consider the words for which feature data are available, an overlap of `r nrow(vocab)` in our data compared to Hills' 130.

## Word2Vec

@@

Using vocabulary obtained by 30 months and the same McRae features as Hills, we construct networks from perceptual and conceptual features. We track the number of features that generate each edge.

```{r message=FALSE}
# perceptual and conceptual McRae features
perceptual_features = c("sound", "taste", "smell", "tactile",
                        "visual-form_and_surface", "visual-motion", "visual-color")
conceptual_features = c("function")

# count shared features between words in vocabulary
perceptual_links <- make_feature_links(vocab = hills_vocab,
                                       feature_types = perceptual_features) %>%
  rename(perceptual = shared)

conceptual_links <- make_feature_links(vocab = hills_vocab,
                                       feature_types = conceptual_features) %>%
  rename(conceptual = shared)

# get word2vec distance between words in vocabulary
w2v_links <- make_w2v_links(vocab = hills_vocab) #TODO still problem w/ vocab matching w2v data

links <- perceptual_links %>%
  full_join(conceptual_links, by=c("from", "to")) %>%
  full_join(w2v_links, by=c("from", "to"))

full_network <- graph_from_data_frame(links, vertices = hills_vocab, directed = FALSE) %>%
  as_tbl_graph()
```

# Results

## The Full Network

### Network statistics and small-world analyses

```{r}
# testing dense layout
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

plot_network(full_network %E>% filter(w2v_similarity >= 0.5), remove_isolated = TRUE, labels=TRUE, frame=TRUE)
```

The full network is shown in the following figure, for w = 1, 2, 3, and 4.

```{r out.width = '100%'}
full_networks = list()
for (w in 1:4) {
  full_networks[[w]] = full_network %E>%
    filter(shared >= w)
}

#par(mfcol=c(2, 2), mar=c(0.5,0.5,0.5,0.5))
for (network in full_networks) {
  plot_network(network, remove_isolated = FALSE, labels=TRUE, frame=TRUE)
}
```

## Basic Vocab and Feature Properties

<!-- ## Basic Network Properties -->

<!-- Some basic properties of networks built from perceptual and conceptual features. -->
<!-- ```{r, results='asis'} -->
<!-- max_w <- 4 -->

<!-- network_properties <- function(networks) { -->
<!--   return( tibble( -->
<!--   name = map_chr(networks, ~ .x$name), -->
<!--   type = map_chr(networks, ~ .x$type), -->
<!--   age = map_dbl(networks, ~ .x$age) %>% -->
<!--     as.integer(), -->
<!--   w = map_dbl(networks, ~ .x$w) %>% -->
<!--     as.integer(), -->
<!--   vertices = map_int(networks, vcount), -->
<!--   edges = map_dbl(networks, ecount) %>% -->
<!--     as.integer(), # for some reason igraph ecount returns double -->
<!--   avg_degree = map(networks, degree) %>% -->
<!--     map_dbl(mean), -->
<!--   avg_shortest_path = map_dbl(networks, mean_distance), -->
<!--   diameter = map_dbl(networks, diameter) %>% -->
<!--     as.integer(), -->
<!--   clustering_coefficient = map_dbl(networks, transitivity), -->
<!--   density = edges / (vertices * (vertices - 1) / 2), -->
<!--   avg_shortest_path_random = 0, # either estimate or calculate values for random nets -->
<!--   diameter_random = 0, -->
<!--   clustering_coefficient_random = density, -->
<!--   isolates = map_dbl(networks, function (g) sum(degree(g) == 0)), -->
<!--   components = map_dbl(networks, count_components) %>% -->
<!--     as.integer() - isolates)) -->
<!-- } -->

<!-- full_networks <- list() -->
<!-- perceptual_networks <- list() -->
<!-- conceptual_networks <- list() -->
<!-- for (w in 1:max_w) { -->
<!--   full_networks[[w]] <- full_network %>% -->
<!--     activate(what = edges) %>% -->
<!--     filter(shared >= w) %>% -->
<!--     set.graph.attribute("w", w) -->

<!--   perceptual_networks[[w]] <- perceptual_network %>% -->
<!--     activate(what = edges) %>% -->
<!--     filter(shared >= w) %>% -->
<!--     set.graph.attribute("w", w) -->

<!--   conceptual_networks[[w]] <- conceptual_network %>% -->
<!--     activate(what = edges) %>% -->
<!--     filter(shared >= w) %>% -->
<!--     set.graph.attribute("w", w) -->
<!-- } -->

<!-- networks <- full_networks %>% -->
<!--   append(perceptual_networks) %>% -->
<!--   append(conceptual_networks) -->

<!-- our_network_properties <- network_properties(networks) -->

<!-- our_network_properties %>% -->
<!--   select(type, w, vertices, edges, avg_degree, diameter, avg_shortest_path, clustering_coefficient) %>% -->
<!--   kable(format="html", -->
<!--         escape = FALSE, -->
<!--         col.names = c("Type", "w", "V", "E", "Average degree", "Diameter", "Average length", "Clustering coefficient"), -->
<!--         digits = 2, -->
<!--         align = rep("l", 8)) %>% -->
<!--   kable_styling(full_width = F) %>% -->
<!--   collapse_rows(columns = 1:3, valign = "top") -->
<!-- ``` -->

<!-- We can compare these networks to those from Hills, noting that we have a different set of words/nodes but that the induced subgraph of those words shared between our analysis and that of Hills should be the same. -->
<!-- ```{r} -->
<!-- hills_network_properties <- tibble( # table from Hills 2009 -->
<!--   type = c(rep("all", times=4), rep("perceptual", times=4), rep("conceptual", 4)), -->
<!--   w = c(1:max_w, 1:max_w, 1:max_w), -->
<!--   clustering_coefficient = c(0.55, 0.54, 0.58, 0.60, 0.54, 0.54, 0.62, 0.62, 0.88, 0.59, 0.38, 1.00), -->
<!--   avg_shortest_path = c(1.72, 2.57, 4.96, 3.22, 1.76, 2.69, 5.02, 2.55, 3.08, 1.59, 5.02, 1.00), -->
<!--   density = c(0.29, 0.10, 0.04, 0.02, 0.27, 0.08, 0.03, 0.01, 0.05, 0.01, 0.0, 0.0), -->
<!--   components = c(1, 1, 4, 10, 1, 2, 8, 11, 7, 14, 7, 2), -->
<!--   isolates = c(0, 6, 20, 47, 0, 10, 31, 69, 33, 81, 113, 126) -->
<!-- ) -->

<!-- # convert contents to text -->
<!-- display_our_properties <- our_network_properties %>% mutate_all(funs(format(., digits=2, trim=TRUE))) -->
<!-- display_hills_properties <- hills_network_properties %>% mutate_all(funs(paste("(", ., ")", sep=''))) -->

<!-- # combine text tables for display -->
<!-- display_properties <- bind_rows(display_our_properties %>% mutate(row = 1:n()), -->
<!--                                 display_hills_properties %>% mutate(row = 1:n())) %>% -->
<!--   group_by(row) %>% -->
<!--   summarise_if(is.character, funs(paste(., collapse=" "))) %>% -->
<!--   arrange(row) -->

<!-- # display combined properties -->
<!-- select(hills_network_properties, type, w) %>% -->
<!--   bind_cols(select(display_properties, clustering_coefficient, avg_shortest_path, -->
<!--                    density, components, isolates)) %>% -->
<!--   kable(format="html", -->
<!--         escape = FALSE, -->
<!--         col.names = c("Type", "w", "Clustering Coefficient", "Average length", "Density", "Components", "Isolates"), -->
<!--         align = rep("l", 7)) %>% -->
<!--   kable_styling(full_width = F) %>% -->
<!--   collapse_rows(columns = 1:2, valign = "top") -->
<!-- ``` -->

<!-- # Clusters -->

<!-- ## Visualize Networks -->
<!-- ```{r out.width = '100%'} -->
<!-- networks <- perceptual_networks[2] -->
<!-- ``` -->

<!-- ## Clique Percolation -->

<!-- Initial Clique Analysis -->
<!-- ```{r out.width = '100%'} -->
<!-- trimmed_networks <- map(networks, function (g) delete.vertices(g, degree(g)==0)) -->

<!-- # cl <- makeCluster(3) -->
<!-- # registerDoParallel(cl) -->
<!-- # getDoParWorkers() -->
<!-- ## Plot with the new colors -->
<!-- for (net in networks) { -->
<!--   for (k in 3:4) { -->
<!--     clusters <- clique.community.opt(net,k) -->
<!--     plot_network(net, clusters = clusters, labels=FALSE) -->
<!--   } -->
<!-- } -->
<!-- # stopCluster(cl) -->
<!-- ``` -->

<!-- Dynamic Visualization -->
<!-- ```{r} -->
<!-- conceptual_clusters <- membership(cluster_walktrap(conceptual_network)) -->

<!-- # Convert to object suitable for networkD3 -->
<!-- conceptual_d3 <- igraph_to_networkD3(conceptual_network, group = conceptual_clusters) -->

<!-- # Create force directed network plot -->
<!-- forceNetwork(Links = conceptual_d3$links, Nodes = conceptual_d3$nodes, -->
<!--              Source = 'source', Target = 'target', NodeID = 'name', -->
<!--              Group = 'group') -->
<!-- ``` -->
